\begin{abstract}
Synthetic 3D scenes are increasingly used to evaluate vision-language and
embodied agents, but the assets used in those scenes often undergo material
conversion before they can be rendered, shared, or reused by downstream
toolchains. We study MDL-to-UsdPreviewSurface conversion as a controlled
within-simulation perturbation for vision-language grounding and embodied-data
reliability. ConvertAsset preserves USD composition while replacing MDL shader
networks with PreviewSurface approximations, allowing matched original and
converted scene evidence. On four Isaac Sim assets, paired proxy metrics show
high visual fidelity (PSNR 35.52\,dB, SSIM 0.990, LPIPS 0.020) and strong
CLIP/DINOv2 similarity, but these proxies do not determine grounding behavior.
We therefore extend the evaluation to GRScenes: a 15-pair clean visual-QA pool
acts as a pilot preservation control, while a frozen 30-pair target-centered
material-shift stress set tests VLM answer and point consistency. Gemma4
preserves 30/30 target-category answers in both material conditions and scores
27/30 versus 29/30 normalized-1000 point hits; Qwen2.5-VL exposes a different
coordinate preference, scoring better in raw pixel space than under the
requested normalized-coordinate contract. We further attach a selected
NVIDIA-baseline material-effect audit and a scoped official InternNav sanity
run over 99 paired KuJiaLe episodes. The resulting contribution is a
claim-bounded ACL protocol: visual similarity, VLM grounding, material-effect
risk, and embodied-data sanity should be reported as separate gates before
converted synthetic scenes are used for downstream robustness claims.
\end{abstract}
