\section{Conclusion}
\label{sec:conclusion}

This paper reframes synthetic-scene material conversion as a reliability
problem for vision-language grounding and embodied data. ConvertAsset makes the
material intervention controlled: the original USD composition is preserved,
and matched noMDL scenes can be compared against the source condition. The
evidence then shows why proxy visual fidelity is only the first gate. Even when
paired renders have high PSNR, SSIM, LPIPS, CLIP, and DINOv2 similarity, VLM
answer recognition, point grounding, parser coverage, coordinate
interpretation, and visible material shifts can diverge.

The practical outcome is a claim discipline, plus a frozen 30-pair
material-shift stress set. Clean visual-QA pools and material-shift stress
pools are reported separately. Coordinate contracts are frozen before model
scoring. Raw-image coordinate rescoring remains diagnostic when the prompt asks
for normalized coordinates. The effect-level ConvertAsset-vs-NVIDIA matrix
applies the same discipline to material mechanisms: covered GRScenes bins can
support bounded selected qualitative claims, clearcoat is a selected NVIDIA
target-loss case, and procedural texture remains an explicit preservation
limitation.

The official KuJiaLe InternNav route adds 99 paired episodes across three local
official scenes, and the official-scene performance closure adds 18/18
successful original/noMDL fresh-process load/render runs with overlapping
ready-time intervals. These results make the evidence stronger than an image
proxy, but they remain scoped sanity evidence. The ACL claim is therefore
precise: material conversion should be treated as a controlled perturbation in
VLM and embodied-data evaluation, and downstream robustness claims should be
made only after the corresponding evidence gate has been passed.
