\section{Discussion}
\label{sec:discussion}

\paragraph{The ACL contribution is evidence discipline.}
The main result is not that noMDL conversion is always harmless, faster, or
better than NVIDIA's converter. The contribution is a way to make material
conversion visible to VLM and embodied-language evaluation. Visual proxy
metrics, VLM answers, point grounding, coordinate-frame compliance,
material-effect risk, and embodied stack usability are different evidence
layers. A converted scene should pass the layer relevant to the claim being
made.

\paragraph{Model behavior is protocol-dependent.}
The GRScenes stress result shows a useful split. Gemma4 follows the
normalized-1000 coordinate contract on the frozen target-centered stress set,
while Qwen2.5-VL exposes stronger raw-pixel behavior under the same prompt
family. This does not prove that one model is generally better at grounding.
It shows that coordinate contracts and parser coverage must be frozen and
reported before material-conversion deltas are interpreted.

\paragraph{Material mechanisms need explicit boundaries.}
The material-effect audit prevents a common failure mode in conversion papers:
counting static conversion success as visual or task success. The four
GRScenes-covered bins support bounded selected qualitative evidence. Clearcoat
and procedural texture do not. In particular, the clearcoat case is a selected
NVIDIA failure case, not a population failure rate, and procedural texture is a
limitation for both converted conditions.

\paragraph{Embodied evidence remains sanity-level.}
The 99-episode official KuJiaLe InternNav run is important because it moves the
paper beyond image-only proxy evaluation. It shows that the converted scenes
can enter a real official navigation pipeline and produce paired metrics.
However, the result is still scoped to three local official scenes and one
navigation stack. The selected rollout videos are qualitative inspection
evidence, and the official-scene performance table supports loadability rather
than speedup. These boundaries are necessary for an ACL/ARR submission because
overclaiming broad embodied robustness would make the paper easier to reject.

\paragraph{Practical use.}
For synthetic data practitioners, ConvertAsset should be used as a candidate
interoperability route followed by task-specific gates. For VLM grounding, that
means matched original/converted renders, target projection, visual QA, frozen
prompt and coordinate contracts, parser coverage, and paired uncertainty. For
embodied data, it means at least smoke-gated scene opening and paired
downstream sanity metrics before converted scenes are treated as benchmark
equivalent.
