\section{Introduction}
\label{sec:introduction}

Vision-language and embodied-language models are increasingly evaluated in
simulated 3D environments where agents must connect text to objects,
viewpoints, and actions. These evaluations often treat the rendered scene as a
stable substrate. In practice, however, scene assets are frequently converted
across material systems before they can be rendered at scale, distributed,
exported to other viewers, or reused by downstream robotics stacks. A seemingly
engineering-level conversion can therefore become a hidden intervention in the
benchmark itself.

We study this problem in NVIDIA Isaac Sim, where photorealistic assets commonly
use Material Definition Language (MDL) shaders while portable USD and glTF-style
pipelines usually expect UsdPreviewSurface or PBR-like materials. Converting
MDL materials to UsdPreviewSurface can improve interoperability, but it can also
change color, reflectance, lighting response, or texture cues. For a
vision-language grounding benchmark, the key question is not only whether two
renders look similar by pixel or feature metrics, but whether a model still
answers the same object query and points to the same target after the material
representation changes.

This paper treats material conversion as a controlled within-simulation
perturbation. We ask: \emph{when synthetic-scene assets are converted for
toolchain compatibility, what evidence is needed before using the converted
renders or scenes for language-grounding and embodied-data claims?} The answer
matters for embodied-language benchmarks such as
GRScenes~\cite{Wang2024GRUtopia}, where downstream experiments may combine
large USD scenes, object-level goals, VLM prompting, and navigation frameworks
such as InternNav/DualVLN~\cite{Wei2026Ground}.

Our current evidence base has two layers. First, we quantify the conversion on
four Isaac Sim furniture assets with paired visual quality, rendering
performance, and CLIP/DINOv2 feature similarity. These measurements show that
the conversion can preserve the dominant visual and feature-level structure of
the tested assets, while runtime effects depend strongly on scene scale.
Second, we build a GRScenes VLM grounding route using a read-only benchmark
source tree, a scratch no-MDL conversion, matched original/converted renders,
target projection, blind visual QA, and local Gemma4/Qwen2.5-VL probes.

The VLM and embodied results are intentionally separated by claim boundary. A
15-pair clean visual-QA pool remains a pilot preservation control:
answer-level recognition can be stable for one backend, while point grounding
remains sensitive to the coordinate contract. A larger frozen 30-pair stress
pool asks a different question: when the target remains visible but material,
color, or lighting changes are apparent, does a VLM still answer and point
consistently? Gemma4 is stable under the normalized-1000 stress protocol, while
Qwen2.5-VL exposes a different raw-coordinate preference. Separately, a
99-episode official KuJiaLe InternNav run checks whether converted scenes remain
usable in a real navigation stack, without promoting the result to a broad
embodied benchmark.

We make four contributions:
\begin{enumerate}
    \item We frame MDL-to-UsdPreviewSurface conversion as a measurable
    within-simulation perturbation for VLM grounding evaluation, rather than
    only as an asset-optimization step.
    \item We define a claim-bounded paired grounding protocol for synthetic
    scenes: immutable benchmark inputs, scratch conversion, matched
    original/noMDL renders, target projection, visual QA, prompt contracts, and
    explicit coordinate-frame scoring.
    \item We instantiate the protocol on GRScenes with a clean preservation
    pilot and a frozen 30-pair target-centered material-shift stress set,
    showing that answer accuracy, point grounding, and coordinate compliance
    can diverge across model backends.
    \item We attach material-effect and embodied-data sanity evidence to the
    same claim registry: a selected NVIDIA-baseline material audit, a
    99-episode official KuJiaLe InternNav sanity run, and repeated official
    scene load/render stability checks. These support bounded reliability
    claims, not broad embodied-benchmark or speedup claims.
\end{enumerate}
