\section{Method}
\label{sec:methodology}

\subsection{Material Conversion as the Intervention}
\label{sec:conversion_intervention}

The intervention is MDL-to-UsdPreviewSurface conversion inside the same USD
scene family. ConvertAsset starts from a root USD file, recursively discovers
referenced layers, payloads, variants, and clips, and writes sibling
\texttt{*\_noMDL.usd} assets rather than flattening the scene. Composition arcs
are rewritten to point to converted siblings, while the original source tree is
kept read-only for benchmark provenance.

Within each processed USD file, MDL-driven materials are replaced with
UsdPreviewSurface networks using the channels that can be represented
portably: base color, roughness, metallic, and normal. Texture inputs are
resolved relative to their declaring layer when possible; otherwise constant
fallbacks are used. This representation deliberately cannot encode every MDL
effect. Clearcoat, procedural textures, displacement, opacity, emission, and
other specialized material mechanisms therefore become risk categories that
must be audited rather than assumed preserved.

\subsection{Evidence Gates}
\label{sec:evidence_gates}

We organize the evaluation as four evidence gates. The first gate measures
paired proxy similarity on four Isaac Sim furniture assets: PSNR, SSIM, LPIPS,
CLIP similarity, DINOv2 similarity, and headless load/render behavior. This
gate checks that the conversion can preserve obvious visual structure in a
controlled single-object setting.

The second gate is the ACL-facing VLM grounding protocol on GRScenes. We use
the original GRScenes tree as the source condition, materialize noMDL
counterparts in a scratch workspace, render matched target-centered views, and
project target bounding boxes into each image. Visual QA separates clean
PASS-only pairs from target-visible PASS/WARN material-shift pairs. Local VLM
backends are prompted to return a target-category answer and a point location.
We score answer match, point-in-box under normalized-1000 coordinates, and a
raw pixel-space diagnostic because coordinate semantics proved model-dependent.

The third gate audits material mechanisms and the NVIDIA baseline. For the
selected GRScenes material-effect pool, we compare original MDL, ConvertAsset
noMDL, and NVIDIA Asset Converter PreviewSurface outputs when all three
conditions pass static gates. For missing material bins, we use bounded
supplemental wrapper fixtures, but only as selected failure or limitation
evidence.

The fourth gate checks embodied-data usability. We run the official
InteriorAgent / KuJiaLe \texttt{val\_unseen} route through
InternNav/DualVLN~\cite{Wei2026Ground} on matched original and noMDL scenes,
and separately measure repeated official-scene load/render stability. These
runs are treated as scoped sanity evidence: they show that the converted scenes
can be exercised by a real embodied stack, but they are not broad navigation
benchmark evidence.
Table~\ref{tab:acl_evidence_gate_registry} summarizes the allowed claim
boundary for each gate.

\input{tables/tab_acl_evidence_gate_registry}

\subsection{Claim Registry}
\label{sec:claim_registry}

Every major result is tied to a manifest, table, or claim entry under
\texttt{paper/shared/evidence}. The registry records not only the supported
claim, but also its scope and forbidden promotion. This is part of the method:
we use conversion as a controlled perturbation, then prevent proxy metrics,
selected videos, or single-scene results from being promoted into broader
robustness claims.
