\section{Related Work}
\label{sec:related_work}

\paragraph{Vision-language grounding and navigation.}
Vision-language navigation connects natural-language instructions to visual
observations and actions. The Room-to-Room benchmark introduced this setting in
real indoor environments~\cite{Anderson2018Vision}, and REVERIE further couples
navigation with remote object identification from referring
instructions~\cite{Qi2020REVERIE}. Recent multimodal LLMs also expose explicit
referential or coordinate-style interfaces, including Shikra's natural-language
coordinate input/output~\cite{Chen2023Shikra} and Ferret's open-vocabulary
referring-and-grounding interface~\cite{You2024Ferret}. Our work is not a new
VLM architecture or a new VLN benchmark. It studies a lower-level reliability
question that these evaluations often assume away: whether a material-converted
synthetic scene still supports the same answer and point-grounding evidence as
the original render.

\paragraph{Embodied simulation and synthetic scene benchmarks.}
Embodied AI platforms such as Habitat~\cite{Savva2019Habitat},
AI2-THOR~\cite{Kolve2017AI2THOR}, and ThreeDWorld~\cite{Gan2021ThreeDWorld}
provide interactive environments for visual and language-conditioned agents.
Isaac Sim and Isaac Lab use USD scenes, RTX rendering, and MDL material graphs
for robotics simulation~\cite{Mittal2023Orbit,Mittal2025Isaac}. GRUtopia and
GRScenes extend this ecosystem to city-scale general-robot scenes and
language-conditioned tasks~\cite{Wang2024GRUtopia}, while InternNav/DualVLN
adds a dual-system foundation-model route for vision-language
navigation~\cite{Wei2026Ground}. We use these ecosystems as evaluation
substrates, but keep the claim scoped: our official KuJiaLe evidence is an
embodied-data sanity check over matched original/noMDL scenes, not a claim that
all InteriorNav or GRScenes navigation behavior is preserved.

\paragraph{Synthetic rendering shifts.}
Prior sim-to-real work shows that rendering choices influence downstream
perception and policy learning. Domain randomization varies textures and
lighting to improve transfer~\cite{Tobin2017Domain,Tremblay2018Training}, and
photorealistic rendering can improve downstream detection in some
settings~\cite{Zakharov2022Photo}. Synthetic-data systems such as SynTable and
Synthetica use Isaac/Omniverse-style rendering pipelines for large-scale robot
perception data~\cite{Ng2023SynTable,Singh2025Synthetica}. We study a
different but related shift: a within-simulation material representation change
from MDL to UsdPreviewSurface, holding geometry and task labels fixed where the
protocol allows.

\paragraph{Proxy metrics versus task evidence.}
Perceptual and feature metrics such as SSIM~\cite{Wang2004Image},
LPIPS~\cite{Zhang2018Unreasonable}, CLIP~\cite{Radford2021Learning}, and
DINOv2~\cite{Oquab2023DINOv2} are useful diagnostics for visual preservation.
However, language-grounding models produce structured outputs whose behavior
depends on prompt contracts, parser coverage, coordinate frames, and visual
salience. Our contribution is therefore a gated evidence protocol: proxy visual
similarity is reported, but VLM answer consistency, point-in-box scoring,
coordinate ablations, material-effect risk, and embodied-data sanity checks
are kept as separate evidence layers.
