\section{Introduction}
\label{sec:introduction}

Physics-based simulation has become indispensable for training and evaluating
robot perception and manipulation systems. Platforms such as NVIDIA Isaac
Sim~\cite{Mittal2025Isaac,Mittal2023Orbit,Makoviychuk2021Isaac} leverage
Universal Scene Description (USD) as a scene representation and GPU-accelerated
ray tracing to produce photorealistic synthetic data at scale. Recent efforts
demonstrate that millions of high-fidelity rendered images can train competitive
object detectors~\cite{Singh2025Synthetica} and instance segmentation
models~\cite{Ng2023SynTable} without any real-world labels, making the
rendering pipeline a critical component of modern sim-to-real transfer.

A key contributor to the visual realism of Isaac Sim is NVIDIA's Material
Definition Language (MDL), which provides physically based shading with
multi-layer effects, subsurface scattering, and procedural noise functions.
However, MDL materials carry clear interoperability costs: they require the
NVIDIA Omniverse runtime and produce assets incompatible with many standard 3D
tools and web viewers that expect UsdPreviewSurface or PBR glTF materials.
Whether MDL also incurs meaningful runtime overhead relative to
UsdPreviewSurface depends on workload and scene scale, and has not been
systematically quantified. Practitioners who generate synthetic training data
at scale~\cite{Singh2025Synthetica,Ng2023SynTable} or deploy digital twins in
resource-constrained settings therefore face a recurring question:
\emph{can we simplify MDL materials to UsdPreviewSurface without degrading the
downstream utility of the rendered images, and under what workloads does such
conversion materially affect runtime behavior?}

Despite the widespread use of Isaac Sim in the robotics and computer vision
communities, no prior work has systematically quantified the consequences of
this material simplification. The sim-to-real gap literature focuses on
the boundary between simulated and real images~\cite{Tobin2017Domain,Tremblay2018Training,Zakharov2022Photo}, but largely ignores the
\emph{within-simulation} rendering gap introduced by material representation
choices. This gap is particularly insidious because it operates silently inside
the data generation pipeline: a practitioner may convert assets for portability
or presumed efficiency gains, unaware of any impact on the training signal.

In this paper we address this gap with three contributions:
\begin{enumerate}
    \item We present an initial multi-level quantification of
    MDL-to-UsdPreviewSurface material simplification trade-offs in NVIDIA Isaac
    Sim, spanning pixel-level image quality
    (PSNR, SSIM~\cite{Wang2004Image}, LPIPS~\cite{Zhang2018Unreasonable}),
    rendering performance, and semantic feature preservation
    (CLIP~\cite{Radford2021Learning} and
    DINOv2~\cite{Oquab2023DINOv2} cosine similarity).
    \item We derive preliminary decision guidelines for synthetic data
    practitioners: under what conditions material simplification is safe, and
    when full-fidelity MDL rendering remains necessary.
    \item We release an open-source conversion toolkit (available upon acceptance) that
    automates the MDL-to-UsdPreviewSurface conversion pipeline with
    composition-preserving USD traversal, texture remapping, and optional mesh
    simplification and GLB export.
\end{enumerate}
